### 2022-12-21 README.Rmd
Updated reanme with new name

We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

>>>>

We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `{Zelig}`'s `setx()` and `setx1()` functions, using `sim_setx()`:
